Constraining Quiescent Supermassive Black Hole Environments.

### 2014-08-22 ms.tex
Adding some description of sample/fixing compilation errors.

\newcommand{\dxdy}[2]{\frac{\partial #1}{\partial #2} }
\newcommand{\ddr}[1]{\dxdy{#1}{r}}
\newcommand{\drhodt}{\dxdy{\rho}{t}}
\newcommand{\dpdr}{\dxdy{p}{r}}
\newcommand{\dvdr}{\dxdy{v}{r}}
\newcommand{\dsdr}{\dxdy{s}{r}}
\newcommand{\dphidr}{\dxdy{\Phi}{r}}
\newcommand{\ke}{\frac{v^2}{2}}
\newcommand{\kew}{\frac{v_w^2}{2}}
\newcommand{\gammaf}{\frac{\gamma}{\gamma-1}}
\newcommand{\gammafi}{\frac{\gamma-1}{\gamma}}
\newcommand{\cs}{\frac{p}{\rho}}
\newcommand{\Q}{q (\ke+\kew-\gammaf \cs)}
\newcommand{\kb}{k_{\rm b}}
\renewcommand{\mp}{m_{\rm p}}
\newcommand{\Menc}{M_{\rm enc}}
\newcommand{\rhostar}{\rho_*}
\newcommand{\Mstar}{M_{\star}}
\newcommand{\Mbh}[1][]{M_{\bullet#1}}
\newcommand{\phirs}{\frac{G \Menc}{\rs}}
\newcommand{\soi}{\rm soi}
\newcommand{\ff}{\rm ff}
\newcommand{\rsoi}{r_{\soi}}
\newcommand{\rIa}{r_{\rm Ia}}
\newcommand{\sigsoi}{\sigma_{\soi}}
\newcommand{\vwO}{v_{w,0}}
\newcommand{\kewO}{\frac{\vwO^2}{2}}
\newcommand{\x}{\frac{r_s}{\rsoi}}
\newcommand{\vwNorm}{\frac{\vwO}{\sigsoi}}
\newcommand{\pyear}{{\rm yr}^{-1}}

@@

\section{Sample}
Describe WM/Nuker sample here.

\section{Model}
We use the same model as \citealt{Quataert:2004a} to find a steady state gas density near the SMBH for each of the galaxies within our sample.  Gas is supplied by winds from the stellar population in the galactic center. Assuming a rate of mass injection, $q$, spherical symmetry and an ideal gas equation of state.

@@

Also, MSPs may also be dissociated in the galactic center...
%%Also low thermalization efficiency inferred in 47 Tuc by Naiman et al.
\end{enumerate}

\item \emph{Type Ia SNe} From he energy injected per Ia SNe, $E_{\rm Ia}d}$ ergs, and the SNe rate,  $R_{\rm Ia}

@@

There will be some radius, $r_{\rm Ia}$, where the dynamical timescale of the flow becomes comparable to the time between successive Type Ia SNe.  If the stagnation radius ($\rs$) of the flow is outside of $\rIa$ then SNes will provide a steady contribution to $\vwO$

@@

\begin{align}
t_{\rm Ia} \sim 2.5 \times 10^5  \Mstar_{,8}^{-1} \; {\rm yrs}.
\end{align}

@@

\begin{align}
 t_{\rm dyn} \sim r/\sigma \sim G M_\star/\sigma^3 \sim 5 \times 10^4 \Mstar_{,8} \sigma_{200}^{-3} \; {\rm yrs}.
\end{align}

@@

\begin{align}
 r_{\rm Ia} \sim G \Mstar_{\rm Ia}/\sigma^2 \sim 4 \sigma_{200}^{-1/2} \; {\rm pc}
\end{align}

The stagnation radius scales linearly with $\Mbh$ (see Equation~\ref{eq:stag_simple}), while the $\rIa$ is roughly constant. For small $\Mbh$, $\rs$ is well inside $\rIa$ and SNes will not contribute to the $\vwO$.  Above $10^8 \Msun$ SNes will represent an important contribution to the overall heating. Thus, for $\Mbh=10^6 \MSun$, we may have $\vwO\simeq 100$ km/s with heating mostly coming from main sequence winds. On the other hand, for $\Mbh \gsim 10^8 \MSun$, we may have $\vwO\simeq 500$ km/s, with the main contribution coming from type Ia SNe. These two regimes are illustrated in Figure~\ref{fig:vw_eff}.

@@

\[
\Lambda(T)\simeq
\begin{cases}
    2.3 \times 10^{-24} \left(T/10^6 \text{K}\right)^{0.5} $erg cm$^3 $s$^{-1}& \text{if } T \gsim 2 \times 10^7 \text{K} \\
    1.1 \times 10^{-22} \left(T/10^6 \text{K}\right)^{-0.7}  $erg cm$^3 $s$^{-1}}& \text{if } T \lsim 2 \times 10^7 \text{K}     
\end{cases}
\label{eq:cooling}
\]

>>>>

\newcommand{\dxdy}[2]{\frac{\partial #1}{\partial #2} }
\newcommand{\ddr}[1]{\dxdy{#1}{r}}
\newcommand{\drhodt}{\dxdy{\rho}{t}}
\newcommand{\dpdr}{\dxdy{p}{r}}
\newcommand{\dvdr}{\dxdy{v}{r}}
\newcommand{\dsdr}{\dxdy{s}{r}}
\newcommand{\dphidr}{\dxdy{\Phi}{r}}
\newcommand{\ke}{\frac{v^2}{2}}
\newcommand{\kew}{\frac{v_w^2}{2}}
\newcommand{\gammaf}{\frac{\gamma}{\gamma-1}}
\newcommand{\gammafi}{\frac{\gamma-1}{\gamma}}
\newcommand{\cs}{\frac{p}{\rho}}
\newcommand{\Q}{q (\ke+\kew-\gammaf \cs)}
\newcommand{\kb}{k_{\rm b}}
\renewcommand{\mp}{m_{\rm p}}
\newcommand{\Menc}{M_{\rm enc}}
\newcommand{\rhostar}{\rho_*}
\newcommand{\Mstar}{M_{\star}}
\newcommand{\Mseight}{M_{\star,8}}
\newcommand{\Mbh}[1][]{M_{\bullet#1}}
\newcommand{\phirs}{\frac{G \Menc}{\rs}}
\newcommand{\soi}{\rm soi}
\newcommand{\ff}{\rm ff}
\newcommand{\rsoi}{r_{\soi}}
\newcommand{\rIa}{r_{\rm Ia}}
\newcommand{\sigsoi}{\sigma_{\soi}}
\newcommand{\vwO}{v_{w,0}}
\newcommand{\kewO}{\frac{\vwO^2}{2}}
\newcommand{\x}{\frac{r_s}{\rsoi}}
\newcommand{\vwNorm}{\frac{\vwO}{\sigsoi}}
\newcommand{\pyear}{{\rm yr}^{-1}}

@@

\section{Sample}
We start with a sample of 61 galaxies from \citetalias{WangMerritt:2004a}, as subset of a larger sample of galaxies from \citealt{FaberTremaine+:1997a}. These are nearby elliptical galaxies, observed with the Hubble WFPC2.

For each galaxy in the sample we take the surface brightness parameterization given in Table 1 of  \citetalias{WangMerritt:2004a}. The parameterization is a Nuker law

\begin{equation}
I(\xi)=I_b 2^{(\beta-\Gamma)/\alpha} \xi^{-\Gamma} (1+\xi^\alpha)^{-(\beta-\Gamma)/\alpha}, \xi=\frac{r}{r_b}.
\end{equation}

This is a broken power law which transitions from an inner power law slope, $\gamma$, to an outer power law slope, $\beta$, at a break radius, $\rb$.

From the surface brightness profile, we follow the same procedure as \citetalias{WangMerritt:2004a} to compute the spatial stellar density and stellar mass profile, both of which are used in our model.

%%AG--some discussion of alternate parameterizations.  My intuition is that for our purposes the parameterization should not matter. But some discussion of alternate possibilities could prevent Alistar Graham from yelling at us.

\section{Model}
\label{sec:model}
We use the same model as \citealt{Quataert:2004a} to find a steady state gas density near the SMBH for each of the galaxies within our sample.  Gas is supplied by winds from the stellar population in the galactic center. Assuming a rate of mass injection, $q$, spherical symmetry and an ideal gas equation of state.

@@

Also, MSPs may also be dissociated in the galactic center...
%%Also low thermalization efficiency inferred in 47 Tuc by Naiman et al.

\item \emph{Type Ia SNe} From he energy injected per Ia SNe, $E_{\rm Ia}$, and the SNe rate,  $R_{\rm Ia}$

@@

There will be some radius, $\rIa$, where the dynamical timescale of the flow becomes comparable to the time between successive Type Ia SNe.  If the stagnation radius ($\rs$) of the flow is outside of $\rIa$ then SNes will provide a steady contribution to $\vwO$

@@

\begin{align}
t_{\rm Ia} \sim 2.5 \times 10^5 \Mseight^{-1} \; {\rm yrs}.
\end{align}

@@

\begin{align}
 t_{\rm dyn} \sim r/\sigma \sim G \Mstar/\sigma^3 \sim 5 \times 10^4 \Mseight \sigma_{200}^{-3} \; {\rm yrs}.
\end{align}

@@

\begin{align}
 r_{\rm Ia} \sim G \Mstar{}_{,\rm Ia}/\sigma^2 \sim 4 \sigma_{200}^{-1/2} \; {\rm pc}
\end{align}

The stagnation radius scales linearly with $\Mbh$ (see Equation~\ref{eq:stag_simple}), while the $\rIa$ is roughly constant. For small $\Mbh$, $\rs$ is well inside $\rIa$ and SNes will not contribute to the $\vwO$.  Above $10^8 \Msun$ SNes will represent an important contribution to the overall heating. Thus, for $\Mbh=10^6 \Msun$, we may have $\vwO\simeq 100$ km/s with heating mostly coming from main sequence winds. On the other hand, for $\Mbh \gsim 10^8 \Msun$, we may have $\vwO\simeq 500$ km/s, with the main contribution coming from type Ia SNe. These two regimes are illustrated in Figure~\ref{fig:vw_eff}.
\end{enumerate}

@@

\[
\Lambda(T)\simeq
\begin{cases}
    2.3 \times 10^{-24} \left(T/10^6 \text{K}\right)^{0.5} $erg cm$^3 $s$^{-1}& \text{if } T \gsim 2 \times 10^7 \text{K} \\
    1.1 \times 10^{-22} \left(T/10^6 \text{K}\right)^{-0.7}  $erg cm$^3 $s$^{-1}& \text{if } T \lsim 2 \times 10^7 \text{K}     
\end{cases}
\label{eq:cooling}
\]
